GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-05-31 paper/main.tex
complete related work first part

    To evaluate the performance of the proposed algorithm, this paper compared 
    it with several NAS algorithms, including weight-sharing methods, 
    non-weight-sharing methods, and neural architecture search without training (NASWOT). 
    We expect develope a faster and more accurate training-free NAS algorithm.

@@

    To overcome this challenge, recent works developed and proposed lots 
    of method which is so called training-free NAS. 
    % NINASWOT
    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed the 
    measurement of the correlation between the binary activation paterns, 
    induced by the untrained network at two inputs, named as neural architecture 
    search without training (NASWOT). 
    Later, Wu et al. \cite{10.1145/3491396.3506510} found a high score 
    obtained by such a function may not correspond to a high-performence 
    model. Thus, they additionally applied noisy immunity method on NASWOT, 
    named as noisy immunity for NASWOT (NINASWOT).
    % NTK
    For another example, Chen et al. proposed to compute the condition 
    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2102.11535} 
    \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
    which is used as the score to estimate the trainability of an architecture.
	% unknown

% what is unknown?
    However, most of score functions suffer from low correlation between 
    score value and the result of an architecture, leading to a predicament 
    that no matter how good the search method is used, we can hardly find 
    an optimal architecture. 
    The major problem causes the low correlation is that a single score 
    function can only evaluate one perspect/characteristic of an architecture.

% method
    To address the problem, we propose cooperating three heterogeneous score 
    functions with genetic-based search method, which evaulate an architecture 
    from different aspects. More specifically, the first score function is 
    NINASWOT \cite{10.1145/3491396.3506510} as an indicator of the ability 
    to distinguish two images. The second one is the condition number of NTK 
    \cite{https://doi.org/10.48550/arxiv.2102.11535} as score to estimate the 
    trainability of an architecture. The last one is (TBD).

% conclusion
    The major contribution of this paper can be summarized as follow:
    \begin{itemize}
        \item Develope a genetic-based neural architecture search method based on three hybrid score functions.
        \item Cooperating three score functions to get a higher correlation between score and accuracy.
    \end{itemize}
    % expect what

    The remainder of this paper is organized as follows: Section 2 provides the 
    detail about the three heterogeneous score functions. Section 3 gives a detailed 
    description about the proposed method. Section 4 provide the simulation results 
    in different search space. The conclusion and further prospect are gived in 
    Section 5.

    \section{Related Works}
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
        \caption{A simple example to illustrate the procedure of NASWOT.}
        \label{fig:naswot}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    In these days, the studies of training-free neural architecture search (NAS) 
    go viral, since the ability to accelerate the procedure for designing a neural 
    network architecture used on specific application, while additionally, 
    training-free NAS cleverly avoid the drawback of long-time training by using 
    various training-free score functions.

    % naswot
    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
    score function without the requirement for training. Here we call it neural 
    architecture search without training (NASWOT) score function. \xfig{fig:naswot} 
	gives a simple example to illustrate the procedure of NASWOT score function. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
    architecture as $f(x_i)$. The activated ReLU units in every layer of the architecture 
    form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix 
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$. 
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow: 
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.

    % ninaswot
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
        \caption{A simple example to illustrate the procedure of noise immunity.}
        \label{fig:ni}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
    found, in some case, an architecture with high score may put different 
    input data, which are originally in the same class, to different classes. 
    To fix this defect, Wu et al. proposed using noise immunity to additionally 
    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
    noise immunity score evaluate an architecture. The score function picks a 
    mini-batch of data, denoted $X$, and then applies Gaussion noise on it, 
    denoted $X'$ and defined by $X'=X+z$ where $z$ is the Gaussion noise. 
    By passing $X$ and $X'$ through the untrained architecture, the sum of the 
    square differences between outputs 
    $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
    $O'=\begin{matrix}o_1',o_2',\cdots,o_C'\end{matrix}$ can be calculated as 
    follows: 
    \begin{equation}
        n=-\sum^C_{n=1}(o_i-o_i')^2
    \end{equation}
    where $C$ is the number of classes determined by the input data.
    According to the experiment outcome of Wu et al., noise immunity can separate 
    those are unable to distinguish $X$ and $X'$ from architectures with high NASWOT 
    score, which just complements the NASWOT score funcion.

    % ntk
    On the other hand, instead of using the correlation of binary activation 
    patterns as score. Chen et al. proposed using the condition number of NTK 
    as an evaluation of the trainability, defined as % add figure
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
    The rationale is based on the work of Lee et al. \cite{Lee_2020} and 
    Xiao et al. \cite{https://doi.org/10.48550/arxiv.1912.13053}, which concluded briefly here, 
    the training dynamics of a wide neural network can be written in terms of the 
    spectrum of the NTK:
    \begin{equation}\label{eq:6}
        \mu_t(\textbf{X}_{\textrm{train}})_i=(\textbf{I}-e^{-\eta\lambda_it})\textbf{Y}_{\textrm{train,}i}
    \end{equation}
    where $\lambda_i$ are the eigenvalues of $\hat\Theta_{\textrm{train}}$ 
    and they're ordered as $\lambda_0\geq\cdots\geq\lambda_m$. 
    According to the hypothesis proposed by Lee et al. \cite{Lee_2020}, the maximum 
    feasible learning rate scale as $\eta\sim2/\lambda_0$. Plug this scaling for 
    $\eta$ in Eq. \ref{eq:6}, we see that the $\lambda_m$ will converge exponentially 
    at a rate given by $1/K_N$ where $K_N=\frac{\lambda_0}{\lambda_m}$.
    Then it can be concluded that if $K_N$ is lower, the corresponding architecture is 
    more trainable.

	% synflow?

    % conclusion

    \section{the proposed algorithm}
    In our work, however, we use rank-based GA. Rather than use single fitness to select, 
    the method preserve the top 1 in NINASWOT score and also the top 1 in the condition 
    number of NTK. After the evolution,

>>>>

    To evaluate the performance of the proposed algorithm, this paper compared 
    it with several NAS algorithms, including weight-sharing methods, 
    non-weight-sharing methods, and several state-of-the-art training-free score 
    functions. 
    The final result shows that in big search space, like nats-bench sss, the 
    proposed algorithm outperforms most of NAS methods.

@@

    To overcome this challenge, recent works developed and proposed lots 
    of method which is so called training-free NAS. 
    % NASWOT
    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed the 
    measurement of the correlation between the binary activation paterns, 
    induced by the untrained network at two inputs, named as neural architecture 
    search without training (NASWOT). 
    % logsynflow
    On the other hand, Lee et al. \cite{lee2019snip} proposed purning parameters based on a saliency matric, 
    which then extended further by Wang et al. \cite{wang2020picking} and Tanaka et al. \cite{tanaka2020pruning}. 
    In \cite{tanaka2020pruning}, Tanaka et al. proposed Iterative Synaptic Flow Pruning 
    (SynFlow) algorithm which intends to deal with the layer collapse problem when purning a network. 
    The score function used in the algorithm is so-called \it{synaptic saliency} \rm{score}. 
    Later, Abdelfattah et al. \cite{abdelfattah2021zerocost} extended SynFlow to score 
    a network architecture by summing synaptic saliency score over all parameters in the model. 
    Cavagnero et al. \cite{Cavagnero_2023} found that SynFlow is likely to suffer from gradient explosion, then 
    proposed the LogSynFlow score function which prevents the problem. 
    % NTK
    For another example, Chen et al. proposed to compute the condition 
    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2102.11535} 
    \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
    which is used as the score to estimate the trainability of an architecture.

% what is unknown?
    However, \xtab{table:corr_score} shows most of score functions suffer from low correlation between 
    score value and the final accuracy of an architecture, leading to a predicament 
    that no matter how good the search method is used, we can hardly find 
    an optimal architecture. 
    The major problem causes the low correlation is that a single score 
    function can only evaluate one perspect/characteristic of an architecture. 
    \begin{table*}[htb]
        \caption{\textsc{The Kendall and Spearman correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
        Each metric has been computed three times with different initialisations and the average is taken as final score. The data is from \cite{Cavagnero_2023}.}}
        \begin{tabular}{ccccccc}\toprule
            Training-free score function & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ 
            \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7} & Kendall & Spearman & Kendall & Spearman & Kendall & Spearman \\ \midrule
            \bf{NTK} & -0.33 & -0.49 & -0.30 & -0.45 & -0.39 & -0.56 \\
            \bf{Snip} & 0.45 & 0.61 & 0.47 & 0.62 & 0.41 & 0.55 \\
            \bf{Fisher} & 0.39 & 0.54 & 0.40 & 0.55 & 0.36 & 0.48 \\
            \bf{Grasp} & 0.28 & 0.41 & 0.35 & 0.50 & 0.35 & 0.49 \\
            \bf{NASWOT} & 0.61 & 0.79 & 0.62 & 0.81 & 0.60 & 0.78 \\
            \bf{SynFlow} & 0.57 & 0.77 & 0.56 & 0.76 & 0.56 & 0.75 \\
            \bf{LogSynFlow} & 0.61 & 0.81 & 0.60 & 0.79 & 0.59 & 0.78 \\ \bottomrule
            \label{table:corr_score}
          \vspace{-\baselineskip}
        \end{tabular}
    \end{table*}

% method
    To address the problem, we propose cooperating three heterogeneous score 
    functions with rank-based search method, which evaulate an architecture 
    from different aspects. More specifically, the first score function is 
    NI \cite{10092788} as an indicator of the ability to distinguish two images. 
    The second one is NASWOT as score to estimate the ability of expression 
    of an architecture. The last one is logsynflow used as the measurement of 
    trainability. 
    By combining these three training-free score functions, this paper also 
    compares the different search algorithms, e.g., random search, genetic 
    algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
    \cite{kirkpatrick1983optimization}.

    % conclusion
    The major contribution of this paper can be summarized as follow:
    \begin{itemize}
        \item Cooperating three score functions to obtain better ability for searching top accuracy neural architectures. 
        \item Develope a rank-based neural architecture search with several search algorithms. 
    \end{itemize}
    % expect what

    The remainder of this paper is organized as follows: \xsec{sec:related_work} provides the 
    detail about the three heterogeneous score functions. \xsec{sec:proposed} gives a detailed 
    description about the proposed method. \xsec{sec:results} begins with parameters setting and 
    provide the simulation results following is the experiment results in different search space. 
    The conclusion and further prospect are gived in \xsec{sec:conclusion}.

    \section{Related Works}
    \label{sec:related_work}
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
        \caption{A simple example to illustrate the procedure of NASWOT.}
        \label{fig:naswot}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    \subsection{Training-free Score Function}
    % naswot
    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
    score function without the requirement for training which is named neural 
    architecture search without training (NASWOT). \xfig{fig:naswot} 
	gives a simple example to illustrate the procedure of NASWOT score function. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
    architecture as $f(x_i)$. The activated ReLU units in every layer of the architecture 
    form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix 
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$. 
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow: 
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.

    % ni
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
        \caption{A simple example to illustrate the procedure of noise immunity.}
        \label{fig:ni}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    Wu et al. \cite{10092788} found, in some case, an architecture with high 
    NASWOT score may classify the same kind of input data into different classes. 
    To fix this defect, Wu et al. proposed using noise immunity (NI) to 
    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
    noise immunity score evaluate an architecture. The score function picks a 
    mini-batch of data, denoted $X$, and then applies Gaussion noise on it. 
    The process can be defined by $X'=X+z$ where $z$ is the Gaussion noise. 
    By passing $X$ and $X'$ through the untrained architecture, then computing 
    the difference of square of each feature maps captured at all pooling layers, 
    denoted $\eta$. According to the fact that the input data are the same kind, 
    the small $\eta$ the better the noise immunity of the architecture is.

    % logsynflow
    Besides from these two model-dependent aspects, Tanaka et al. \cite{tanaka2020pruning} 
    generalized synaptic saliency scores, and proposed SynFlow algorithm to avoids layer 
    collapse when performing purning. 
    Inspired from \cite{tanaka2020pruning}, \cite{wang2020picking}, \cite{lee2019snip}, 
    Abdelfattah et al. \cite{abdelfattah2021zerocost} proposed summing synaptic saliency scores 
    over all parameters in the model as an accuracy estimator to a architecture.

    Besides from these two model-dependent aspects, roots from The Lottery Ticket Hypothesis 
    \cite{frankle2019lottery}, saliency matric is used on purning network parameters in 
    \cite{lee2019snip}, which can be formula as 
    \begin{equation}
        \label{equ:snip}
        S_p(\theta)=\lvert\frac{\partial \mathcal L}{\partial \theta}\odot\theta\rvert
    \end{equation}
    where $\mathcal L$ is the loss function of a neural network with parameters $\theta$ 
    and $\theta$ is the Hadamard product. 
    The saliency matric approximates the change in loss when purning a specific parameters.
    Later, Wang et al. \cite{wang2020picking} approximates the change in gradient norm when 
    purning the network, which defined as 
    \begin{equation}
        \label{equ:grap}
        S_p(\theta)=-(H\frac{\partial \mathcal L}{\partial \theta})\odot\theta
    \end{equation}
    where $\mathcal L$ is the change in gradient norm instead of loss function and $H$ is 
    the Hessian. 
    In \cite{tanaka2020pruning}, Tanaka et al. generalized the synaptic saliency scores as 
    \begin{equation}
        \label{equ:synflow}
        S_p(\theta)=\frac{\partial \mathcal L}{\partial \theta}\odot\theta
    \end{equation}
    which is named SynFlow. 
    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, conclude that summing 
    synaptic saliency score over all parameters in the model can be used to score a network 
    architecture, which is formula as
    \begin{equation}
        \label{equ:zero_cost}
        S_n=\sum^N_i S_p(\theta)_i
    \end{equation}
    Finally, Cavagnero et al. \cite{Cavagnero_2023} imporved SynFlow, which is likely to fall into 
    gradient explosion problem, and proposed LogSynFlow score function, simply scaling down the gradient. 
    The formula is defined by 
    \begin{equation}
        \label{equ:logsynflow}
        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1)
    \end{equation}

    % conclusion
    \subsection{Search Algorithm}

    \section{The Proposed Algorithm}
    \label{sec:proposed}
    In this work,

    \section{experiment result}
    \label{sec:results}

    \subsection*{natsbenchsss}
    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccl@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
        & & validation & test & validation & test & validation & test \\ \midrule
        &&&&\textbf{Non-weight sharing}&&&\\
        AREA      & $12,000$ & $84.62 \pm \z{0.41}$                & $93.16 \pm 0.16$               & $59.24 \pm \z{1.11}$                 & $69.56 \pm \z{0.96}$                & $37.58 \pm 1.09$                 & $45.30 \pm \z{0.91}$                \\
        REA       & $12,000$ & $90.26 \pm \z{0.22}$                & $93.17 \pm 0.21$               & $69.48 \pm \z{0.76}$                 & $69.49 \pm \z{0.94}$                & $44.84 \pm 0.72$                 & $45.47 \pm \z{0.91}$                \\
        RS        & $12,000$ & $90.08 \pm \z{0.24}$                & $93.01 \pm 0.29$               & $69.14 \pm \z{0.94}$                 & $69.17 \pm \z{1.00}$                & $44.66 \pm 1.02$                 & $44.83 \pm \z{1.05}$                \\
        RL        & $12,000$ & $90.17 \pm \z{0.23}$                & $93.08 \pm 0.21$               & $69.23 \pm \z{0.87}$                 & $69.29 \pm \z{1.08}$                & $44.68 \pm 0.91$                 & $45.05 \pm \z{0.93}$                \\
        BOHB      & $12,000$ & $90.05 \pm \z{0.30}$                & $93.03 \pm 0.20$               & $69.04 \pm \z{0.76}$                 & $69.16 \pm \z{0.90}$                & $44.71 \pm 0.78$                 & $44.91 \pm \z{1.05}$                \\ \midrule
        %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
        &&&&\textbf{Training-free}&&&\\
        NI (N=1,000) & $X$ & $89.56\pm \z{0.147}$ & $92.55\pm 0.187$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        NASWOT (N=1,000) & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        logsynflow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        rk (N=1000) & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        GA-rk & $457.54$ & $90.29\pm \z{0.149}$ & $93.27\pm0.193$ & $69.88\pm \z{0.497}$ & $70.06\pm \z{0.481}$ & $45.57\pm 0.425$ & $46.19\pm \z{0.846}$ \\ 
        SA-rk & $682.36$ & $90.37\pm \z{0.204}$ & $93.29\pm0.182$ & $70.11\pm \z{0.457}$ & $70.32\pm \z{0.458}$ & $45.38\pm 0.499$ & $46.45\pm \z{0.687}$ \\ \bottomrule
        \end{tabular}
        \label{table:overall_sss}
          \vspace{-\baselineskip}
      \end{table*}

    \subsection*{nasbench201}
    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccl@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
        & & validation & test & validation & test & validation & test \\ \midrule
        &&&&\textbf{Non-weight sharing}&&&\\
        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm \z{1.14}$                \\
        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm \z{1.51}$                \\
        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm \z{1.25}$                \\
        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm \z{1.37}$                \\
        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm \z{3.73}$                \\ \midrule
        &&&&\textbf{Weight sharing}&&&\\
        RSWS      & $\z{4,154}$  & $76.95 \pm 16.74$                & $82.60 \pm 12.10$               & $52.51 \pm 18.33$                & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$               \\
        DARTS-V1  & $\z{5,475}$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\
        DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$               & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                & $15.61 \pm \z{0.00}$                   & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\
        GDAS      & $11,183$ & $90.05 \pm \z{0.23}$                & $93.46 \pm \z{0.13}$               & $71.02 \pm \z{0.31}$                 & $70.56 \pm \z{0.24}$                & $41.77 \pm 1.24$                 & $41.96 \pm \z{0.90}$                \\
        SETN      & $16,787$ & $84.25 \pm \z{5.05}$                & $88.01 \pm \z{4.52}$               & $59.72 \pm \z{7.30}$                & $59.91 \pm \z{7.51}$                   & $33.93 \pm 3.85$                 & $33.48 \pm \z{4.22}$                \\
        ENAS      & $\z{7,061}$  & $40.11 \pm \z{3.28}$                & $56.33 \pm \z{3.70}$               & $14.09 \pm \z{1.60}$                 & $14.77 \pm \z{1.45}$                & $16.20 \pm 0.48$                 & $15.93 \pm \z{0.67}$                \\ \midrule
        &&&&\textbf{Training-free}&&&\\
        NI (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        NASWOT (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        logsynflow (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        rk (N=1000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        GA-rk & $747.25$ & $89.93\pm \z{0.196}$ & $93.41\pm0.083$ & $70.70\pm \z{0.417}$ & $70.76\pm \z{0.378}$ & $42.70\pm 1.315$ & $43.10\pm \z{1.428}$ \\ 
        SA-rk & $X$ & $89.95\pm \z{0.194}$ & $93.37\pm0.114$ & $70.69\pm \z{0.391}$ & $70.75\pm \z{0.532}$ & $X\pm X$ & $43.10\pm \z{1.506}$ \\ \bottomrule
        \end{tabular}
        \label{table:overall_201}
          \vspace{-\baselineskip}
      \end{table*}

    \section{Conclusion}
    \label{sec:conclusion}
